---
title: "Untitled"
author: "Carl Frederick"
date: "8/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(sf)
library(contextualDataTool)
library(rmapshaper)
library(pryr)
library(leaflet)
library(tidyverse)

data("wiBlkGrp")
data("dist_maps")

```

## Original Block Group File from tidycensus

```{r}
size10 <- object_size(wiBlkGrp)

colors <- colorQuantile("viridis", wiBlkGrp$lf_unemployed, n = 7)(wiBlkGrp$lf_unemployed)

ts10start <- Sys.time()

wiBlkGrp %>% 
  leaflet() %>% 
    addPolygons(stroke = FALSE, fillOpacity = .5,
                fillColor = colors)

ts10end <- Sys.time()
```

### Keep 90% of points

```{r}
wbg.9 <- ms_simplify(wiBlkGrp, .9)

size9 <- object_size(wbg.9)

colors <- colorQuantile("viridis", wbg.9$lf_unemployed, n = 7)(wbg.9$lf_unemployed)

ts9start <- Sys.time()

wbg.9 %>% 
  leaflet() %>% 
    addPolygons(stroke = FALSE, fillOpacity = .5,
                fillColor = colors)

ts9end <- Sys.time()
```

### Keep 80% of points

```{r}
wbg.8 <- ms_simplify(wiBlkGrp, .8)

size8 <- object_size(wbg.8)

colors <- colorQuantile("viridis", wbg.8$lf_unemployed, n = 7)(wbg.8$lf_unemployed)

ts8start <- Sys.time()

wbg.8 %>% 
  leaflet() %>% 
    addPolygons(stroke = FALSE, fillOpacity = .5,
                fillColor = colors)

ts8end <- Sys.time()
```

### Keep 70% of points

```{r}
wbg.7 <- ms_simplify(wiBlkGrp, .7)

size7 <- object_size(wbg.7)

colors <- colorQuantile("viridis", wbg.7$lf_unemployed, n = 7)(wbg.7$lf_unemployed)

ts7start <- Sys.time()

wbg.7 %>% 
  leaflet() %>% 
    addPolygons(stroke = FALSE, fillOpacity = .5,
                fillColor = colors)

ts7end <- Sys.time()
```

### Keep 60% of points

```{r}
wbg.6 <- ms_simplify(wiBlkGrp, .6)

size6 <- object_size(wbg.6)

colors <- colorQuantile("viridis", wbg.6$lf_unemployed, n = 7)(wbg.6$lf_unemployed)

ts6start <- Sys.time()

wbg.6 %>% 
  leaflet() %>% 
    addPolygons(stroke = FALSE, fillOpacity = .5,
                fillColor = colors)

ts6end <- Sys.time()
```

### Keep 50% of points

```{r}
wbg.5 <- ms_simplify(wiBlkGrp, .5)

size5 <- object_size(wbg.5)

colors <- colorQuantile("viridis", wbg.5$lf_unemployed, n = 7)(wbg.5$lf_unemployed)

ts5start <- Sys.time()

wbg.5 %>% 
  leaflet() %>% 
    addPolygons(stroke = FALSE, fillOpacity = .5,
                fillColor = colors)

ts5end <- Sys.time()
```

### Keep 40% of points

```{r}
wbg.4 <- ms_simplify(wiBlkGrp, .4)

size4 <- object_size(wbg.4)

colors <- colorQuantile("viridis", wbg.4$lf_unemployed, n = 7)(wbg.4$lf_unemployed)

ts4start <- Sys.time()

wbg.4 %>% 
  leaflet() %>% 
    addPolygons(stroke = FALSE, fillOpacity = .5,
                fillColor = colors)

ts4end <- Sys.time()
```

### Keep 30% of points

```{r}
wbg.3 <- ms_simplify(wiBlkGrp, .3)

size3 <- object_size(wbg.3)

colors <- colorQuantile("viridis", wbg.3$lf_unemployed, n = 7)(wbg.3$lf_unemployed)

ts3start <- Sys.time()

wbg.3 %>% 
  leaflet() %>% 
    addPolygons(stroke = FALSE, fillOpacity = .5,
                fillColor = colors)

ts3end <- Sys.time()
```

### Keep 20% of points

```{r}
wbg.2 <- ms_simplify(wiBlkGrp, .2)

size2 <- object_size(wbg.2)

colors <- colorQuantile("viridis", wbg.2$lf_unemployed, n = 7)(wbg.2$lf_unemployed)

ts2start <- Sys.time()

wbg.2 %>% 
  leaflet() %>% 
    addPolygons(stroke = FALSE, fillOpacity = .5,
                fillColor = colors)

ts2end <- Sys.time()
```

### Keep 10% of points

```{r}
wbg.1 <- ms_simplify(wiBlkGrp, .1)

size1 <- object_size(wbg.1)

colors <- colorQuantile("viridis", wbg.1$lf_unemployed, n = 7)(wbg.1$lf_unemployed)

ts1start <- Sys.time()

wbg.1 %>% 
  leaflet() %>% 
    addPolygons(stroke = FALSE, fillOpacity = .5,
                fillColor = colors)

ts1end <- Sys.time()
```

### Keep 5% of points

```{r}
wbg.05 <- ms_simplify(wiBlkGrp, .05)

size05 <- object_size(wbg.05)

colors <- colorQuantile("viridis", wbg.05$lf_unemployed, n = 7)(wbg.05$lf_unemployed)

ts05start <- Sys.time()

wbg.05 %>% 
  leaflet() %>% 
    addPolygons(stroke = FALSE, fillOpacity = .5,
                fillColor = colors)

ts05end <- Sys.time()
```

### Compare Speed/Memory

```{r}
tibble(
  `Points Kept` = scales::percent(c(seq(1, .1, -.1), .05)),
  `Render Time` = c(difftime(ts10start, ts10end),
                    difftime(ts9start, ts9end),
                    difftime(ts8start, ts8end),
                    difftime(ts7start, ts7end),
                    difftime(ts6start, ts6end),
                    difftime(ts5start, ts5end),
                    difftime(ts4start, ts4end),
                    difftime(ts3start, ts3end),
                    difftime(ts2start, ts2end),
                    difftime(ts1start, ts1end),
                    difftime(ts05start, ts05end)),
  `Object Size` = c(size10, size9, size8, size7, size6,
                    size5, size4, size3, size2, size1, size05)
) %>% 
  knitr::kable(., caption = "Stats re: WiBlkGrp")
```

## Original Block Group File from tidycensus

```{r}
size10 <- object_size(dist_maps)

ts10start <- Sys.time()

dist_maps %>% 
  leaflet() %>% 
    addPolygons(weight = 1, color = "gray", fill = FALSE)

ts10end <- Sys.time()
```

### Keep 90% of points

```{r}
wbg.9 <- ms_simplify(dist_maps, .9)

size9 <- object_size(wbg.9)

ts9start <- Sys.time()

wbg.9 %>% 
  leaflet() %>% 
    addPolygons(weight = 1, color = "gray", fill = FALSE)

ts9end <- Sys.time()
```

### Keep 80% of points

```{r}
wbg.8 <- ms_simplify(dist_maps, .8)

size8 <- object_size(wbg.8)

ts8start <- Sys.time()

wbg.8 %>% 
  leaflet() %>% 
    addPolygons(weight = 1, color = "gray", fill = FALSE)

ts8end <- Sys.time()
```

### Keep 70% of points

```{r}
wbg.7 <- ms_simplify(dist_maps, .7)

size7 <- object_size(wbg.7)

ts7start <- Sys.time()

wbg.7 %>% 
  leaflet() %>% 
    addPolygons(weight = 1, color = "gray", fill = FALSE)

ts7end <- Sys.time()
```

### Keep 60% of points

```{r}
wbg.6 <- ms_simplify(dist_maps, .6)

size6 <- object_size(wbg.6)

ts6start <- Sys.time()

wbg.6 %>% 
  leaflet() %>% 
    addPolygons(weight = 1, color = "gray", fill = FALSE)

ts6end <- Sys.time()
```

### Keep 50% of points

```{r}
wbg.5 <- ms_simplify(dist_maps, .5)

size5 <- object_size(wbg.5)

ts5start <- Sys.time()

wbg.5 %>% 
  leaflet() %>% 
    addPolygons(weight = 1, color = "gray", fill = FALSE)

ts5end <- Sys.time()
```

### Keep 40% of points

```{r}
wbg.4 <- ms_simplify(dist_maps, .4)

size4 <- object_size(wbg.4)

ts4start <- Sys.time()

wbg.4 %>% 
  leaflet() %>% 
    addPolygons(weight = 1, color = "gray", fill = FALSE)

ts4end <- Sys.time()
```

### Keep 30% of points

```{r}
wbg.3 <- ms_simplify(dist_maps, .3)

size3 <- object_size(wbg.3)

ts3start <- Sys.time()

wbg.3 %>% 
  leaflet() %>% 
    addPolygons(weight = 1, color = "gray", fill = FALSE)

ts3end <- Sys.time()
```

### Keep 20% of points

```{r}
wbg.2 <- ms_simplify(dist_maps, .2)

size2 <- object_size(wbg.2)

ts2start <- Sys.time()

wbg.2 %>% 
  leaflet() %>% 
    addPolygons(weight = 1, color = "gray", fill = FALSE)

ts2end <- Sys.time()
```

### Keep 10% of points

```{r}
wbg.1 <- ms_simplify(dist_maps, .1)

size1 <- object_size(wbg.1)

ts1start <- Sys.time()

wbg.1 %>% 
  leaflet() %>% 
    addPolygons(weight = 1, color = "gray", fill = FALSE)

ts1end <- Sys.time()
```

### Keep 5% of points

```{r}
wbg.05 <- ms_simplify(dist_maps, .05)

size05 <- object_size(wbg.05)

ts05start <- Sys.time()

wbg.05 %>% 
  leaflet() %>% 
    addPolygons(weight = 1, color = "gray", fill = FALSE)

ts05end <- Sys.time()
```

### Compare Speed/Memory

```{r}
tibble(
  `Points Kept` = scales::percent(c(seq(1, .1, -.1), .05)),
  `Render Time` = c(difftime(ts10start, ts10end),
                    difftime(ts9start, ts9end),
                    difftime(ts8start, ts8end),
                    difftime(ts7start, ts7end),
                    difftime(ts6start, ts6end),
                    difftime(ts5start, ts5end),
                    difftime(ts4start, ts4end),
                    difftime(ts3start, ts3end),
                    difftime(ts2start, ts2end),
                    difftime(ts1start, ts1end),
                    difftime(ts05start, ts05end)),
  `Object Size` = c(size10, size9, size8, size7, size6,
                    size5, size4, size3, size2, size1, size05)
) %>% 
  knitr::kable(., caption = "Stats re: dist_maps")
```

